---
title: "Plot results"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: false
    code_folding: hide
    theme: lumen
---

```{r libraries, warning=F, message=F}
library(dplyr)
library(ggplot2)
library(tidyr)
```

```{r dictionaries}
measureDict <- c(keyGenTime = "key generation",
                 keyGen4HMEkeys = "key gen 4 HME",
                 totEncTime = "total encryption",
                 avgEncTime = "avg encryption",
                 totHomOpr = "total hom. operations",
                 decTime = "decryption",
                 encSize = "encrypted size",
                 encTime = "encryption",
                 opTime = "modyfication op.")
variantDict <- c(`1` = "10 x ADD",
                 `2` = "10 x MUL",
                 `3` = "5x ADD + 5x MUL",
                 `4` = "5x MUL + 5x ADD",
                 `5` = "2x ADD + 7x MUL + 1x ADD",
                 `6` = "1x MUL + 9x ADD",
                 `7` = "1x ADD + 9x MUL",
                 `8` = "1x ADD + 1x MULL ... total 10x",
                 `9` = "3x ADD + 3x MUL + 4x ADD",
                 `10` = "2x MUL + 5x ADD + 1x MUL + 2x ADD")
```


# Eksperymenty pojedyncze {.tabset .tabset-fade .tabset-pills}

## Eksperyment 1

```{r}
results1 <- read.csv2("data/results1.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results1 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  mutate(variant = as.factor(variant)) %>% 
  do(.,.) ->
  df1
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df1 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = numMults,
             color = variant)) +
    facet_grid(measure ~ .,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_jitter()) +
    geom_smooth(linewidth = 0.2) +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to max multiplication depth") + 
    theme_dark()
```


## Eksperyment 2

```{r}
results2 <- read.csv2("data/results2.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results2 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  mutate(variant = as.factor(variant)) %>% 
  do(.,.) ->
  df2
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df2 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = dist,
             color = variant)) +
    facet_grid(measure ~ .,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_jitter()) +
    geom_smooth(linewidth = 0.2,
                method = "glm") +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to noise distribution") + 
    theme_dark()
```


## Eksperyment 3

```{r}
results3 <- read.csv2("data/results3.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results3 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  do(.,.) ->
  df3
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df3 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = securityLevel,
             color = variant)) +
    facet_grid(measure ~ .,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2) +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to security level") + 
    theme_dark()
```


## Eksperyment 4

```{r}
results4 <- read.csv2("data/results4.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results4 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  mutate(ptMod = as.factor(ptMod)) %>% 
  do(.,.) ->
  df4
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df4 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = ptMod,
             color = variant)) +
    facet_grid(measure ~ .,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm",
                mapping = aes(x = as.numeric(ptMod))) +
    coord_cartesian(ylim = c(0, NA)) +
    #scale_x_continuous(trans='log10') +
    ylab("time (ms)") +
    ggtitle("Time to plaintext modulus") + 
    theme_dark()
```


# Eksperymenty mieszane {.tabset .tabset-fade .tabset-pills}

## Eksperyment 5

```{r}
results5 <- read.csv2("data/results5.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results5 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  #mutate(ptMod = as.factor(ptMod)) %>% 
  do(.,.) ->
  df5
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df5 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = numMults,
             color = variant)) +
    facet_grid(measure ~ ptMod,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm") +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to plaintext modulus and numMults") + 
    theme_dark()
```


## Eksperyment 6

```{r}
results6 <- read.csv2("data/results6.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results6 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  #mutate(ptMod = as.factor(ptMod)) %>% 
  do(.,.) ->
  df6
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df6 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = dist,
             color = variant)) +
    facet_grid(measure ~ ptMod,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm") +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to plaintext modulus and dist") + 
    theme_dark()
```


## Eksperyment 7

```{r}
results7 <- read.csv2("data/results7.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results7 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  do(.,.) ->
  df7
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df7 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = numMults,
             color = variant)) +
    facet_grid(measure ~ dist,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm") +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to noise distribution and numMults") + 
    theme_dark()
```


## Eksperyment 8

```{r}
results8 <- read.csv2("data/results8.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results8 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  do(.,.) ->
  df8
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df8 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = numMults,
             color = variant)) +
    facet_grid(measure ~ securityLevel,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm") +
    coord_cartesian(ylim = c(0, NA)) +
    ylab("time (ms)") +
    ggtitle("Time to security level and numMults") + 
    theme_dark()
```


## Eksperyment 9

```{r}
results9 <- read.csv2("data/results9.csv", stringsAsFactors = T, dec = ".")
```

```{r}
results9 %>%
  ##na.omit() %>% 
  ##group_by(ptMod,variant,securityLevel,dist,numMults) %>% 
  ##summarise(across(-nthRep, mean), .groups = "drop", na.rm=T) %>% 
  mutate_if(is.numeric, round, 3)  %>% 
  mutate(variant = as.factor(variant)) %>% 
  mutate(ptMod = as.factor(ptMod)) %>% 
  do(.,.) ->
  df9
```

```{r fig.height=10, fig.width=10, warning=FALSE, message=FALSE}
df9 %>% 
  pivot_longer(keyGenTime:decTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>% 
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  mutate(variant=recode(variant, !!!variantDict)) %>% 
  ggplot(aes(y = time,
             x = ptMod,
             color = variant)) +
    facet_grid(measure ~ securityLevel,
               scales = "free_y") +
    geom_point(size = 1,
               position = position_nudge()) +
    geom_smooth(linewidth = 0.2,
                method = "glm",
                mapping = aes(x = as.numeric(ptMod))) +
    coord_cartesian(ylim = c(0, NA)) +
    #scale_x_continuous(trans='log10') + 
    ylab("time (ms)") +
    ggtitle("Time to security level and plaintext modulus") + 
    theme_dark() + 
    theme(axis.text.x = element_text(angle = -45, hjust = 0))
```


# Porównanie {.tabset .tabset-fade .tabset-pills}

```{r}
resultsCmpr <- read.csv2("data/resultsAes.csv", stringsAsFactors = T, dec = ".")
```

```{r}
resultsCmpr %>%
  ##na.omit() %>% 
  group_by(type,securityLen) %>% 
  summarise(across(, mean), .groups = "drop", na.rm=T) %>% 
  mutate(securityLen = as.character(securityLen)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  do(.,.) ->
  dfCmpr
```

* def - ptMOd=537133057; numMul=3; dist=3.2; variant=8
* best case - ptMOd=5767169; sec=HEStd_128_classic; numMul=1; variant=1
* worst case - ptMOd=549760663553; sec=HEStd_256_classic; numMul=20; variant=2


## Rozmiar danych

```{r fig.height=5, fig.width=5, warning=FALSE, message=FALSE}
dfCmpr %>% 
  ggplot(aes(y = encSize,
             x = securityLen,
             color = type)) +
    facet_grid(. ~ .,
               scales = "fixed") +
    geom_point(size = 3,
               position = position_nudge()) +
    scale_y_continuous(trans = "log10", limits = c(1,NA)) +
    ylab("Size (bytes)") +
    ggtitle("Encrypted data size") + 
    theme_dark()
```


## Czasy przetwarzania

```{r fig.height=5, fig.width=8, warning=FALSE, message=FALSE}
dfCmpr %>% 
  pivot_longer(encTime:opTime,
               names_to = "measure", values_to = "time",
               values_drop_na = F) %>%
  mutate(measure=recode(measure, !!!measureDict)) %>% 
  ggplot(aes(y = time,
             x = securityLen,
             color = type)) +
    facet_grid(. ~ measure,
               scales = "fixed") +
    geom_point(size = 3,
               position = position_nudge()) +
    scale_y_continuous(trans = "log10") +
    ylab("Time (us)") +
    ggtitle("Processing time") + 
    theme_dark()
```


